Real Time Shape Reconstruction for Near Earth Asteroid Landing

### 2018-04-01 abstract.tex
Add some  todo for rest of abstract

The variance for each measurement vector is assumed to be related to the ``distance'' from the measurement to vertex \( \vb{v}_i \).
Here we use the geodesic distance to parameterize the difference, and hence  uncertainty, or associating the measurement with a given vertex.
From spherical trigonometry the central angle between measurement \( \vb{p}_i \) and vertex \( \vb{v}_i \) of the shape estimate is
\begin{align}
    \Delta \sigma_i = \arctan \parenth{\frac{\norm{\vb{p}_i \times \vb{v}_i}}{\vb{p}_i \cdot \vb{v}_i }}.
\end{align}
The variance of measurement \( \vb{p}_i \) with respect to vertex \( \vb{v}_i \) is then defined as the arc length as
\begin{align}
    w_{m, i} = \norm{\vb{p}_i} \Delta \sigma .
\end{align}
This approach relates the uncertainty of the measurement with the distance to a given vertex.
As a result, measurements which are far from a vertex, where \( \Delta \sigma \) is large, will tend to have a larger variance and hence uncertainty.

From Bayes' theorem, the 
Compute angle between measurement and all vertices of shape

@@

@@

\section{Expected Results and Significance}

\subsection{Equations of Motion}

\subsection{Nonlinear Landing Controller}\label{sec:landing}

\section{Expected Results and Significance}\label{sec:expected}

\bibliographystyle{AAS_publication} 
\bibliography{library}

>>>>

The variance for each measurement vector is assumed to be related to the ``distance'' from the measurement to vertex \( \vb{v}_i \).
Here we use the geodesic distance to parameterize the difference, and hence  uncertainty, or associating the measurement with a given vertex.
From spherical trigonometry the central angle between measurement \( \vb{p}_i \) and vertex \( \vb{v}_i \) of the shape estimate is
\begin{align}
    \Delta \sigma_i = \arctan \parenth{\frac{\norm{\vb{p}_i \times \vb{v}_i}}{\vb{p}_i \cdot \vb{v}_i }}.
\end{align}
The variance of measurement \( \vb{p}_i \) with respect to vertex \( \vb{v}_i \) is then defined as the arc length as
\begin{align}
    w_{m, i} = \norm{\vb{p}_i} \Delta \sigma .
\end{align}
This approach relates the uncertainty of the measurement with the distance to a given vertex.
As a result, measurements which are far from a vertex, where \( \Delta \sigma \) is large, will tend to have a larger variance and hence uncertainty. 
From Bayes' theorem, the a posterior probability is
\begin{align}
    p(\norm{\vb{v}_i} | \norm{\vb{p}_i}) = \frac{p(\norm{\vb{p}_i} | \norm{\vb{v}_i}) p(\norm{\vb{v}_i})}{p(\norm{\vb{p}_i}} \propto p(\norm{\vb{p}_i} | \norm{\vb{v}_i}) p(\norm{\vb{v}_i}).
\end{align}
From the properties of a Gaussian the a posterior probability is also distributed according to a Gaussian distribution
\begin{align}
    Gaussian
\end{align}

When a measurement is far away from a given vertex, the influence of the measurement on the radial position of the vertex is diminished.

Compute angle between measurement and all vertices of shape

@@

Describe the simulation

Assume initial ellipsoid

Vertices are taken from the shape model and serve to emulate measurements from a lidar

Each vertex is added in real time and only those within a certain area/angle are considered

@@

\section{Expected Results and Significance}
Fast way to update mesh

Final paper will demonstrate how to use this updated mesh with the gravity model in the controller

Also compare the gravity of  estimate and truth model
\bibliographystyle{AAS_publication} 
\bibliography{library}
